---
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
params:
  symbol: TSLA
---
  
# `r params$symbol` 

## Summary{.tabset}

```{r, echo=FALSE, message=FALSE}

library(quantmod)
library(dygraphs)

prices <- round(getSymbols(params$symbol, auto.assign = FALSE), 2)
close <- Cl(last(prices))
open <- Op(last(prices))
```

The stock closed `r ifelse(close>open,'up','down')` at `r close` dollars per share yesterday.

### Price History

The chart below is made with the `quantmod` and `dygraphs` R packages.
***
  
```{r echo=FALSE}
dygraphs::dygraph(prices) %>% dyRangeSelector()
```

### Raw Data

The table below displays the daily price data for the stock. We made a concise, interactive table with the `DT` package, a new package for making searchable data tables. 
***
  
```{r echo=TRUE}
DT::datatable(data.frame(prices[, 1:4], 2))
```

## Model{.tabset}

### Plot

This model is fit with the auto.arima function in the forecast package.

```{r, warning=FALSE, message=FALSE}
library(forecast)
m <- auto.arima(prices[,1])
plot(forecast(m,12))
```

### Forecasts
```{r, warning=FALSE, message=FALSE}
f <- forecast(m,12)
```

The forecast for tomorrow is `r as.numeric(f$mean)[1]`.

